---
title: "Table 1 & Descriptive Statistics"
author: "Bailey Hebermehl"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup-bailey, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r bring-in-data, echo=FALSE}
here::i_am("subproject_bailey/report.Rmd")
```

# Table One
Table #1 provides descriptive statistics for the variables of interest in our analysis. 
```{r table-one, echo=FALSE}
table1 <- readRDS(
  file = here::here("subproject_bailey/output/table1.rds")
)
table1
```

# Bar Charts and Histograms for Variables of Interest
The figures below illustrate the distributions of the variables of interest in our study population. As shown in Figure A, 178,670 patients did not have a pneumonia diagnosis, whereas 27,845 patients were diagnosed with pneumonia. Figure B shows that 31,614 patients were not intubated and 6,775 patients underwent intubation. Figure C indicates that 204,973 patients did not have cardiovascular disease, while 4,139 patients did. Figure D shows that 176,997 patients did not have obesity, compared with 32,141 patients who did. Figure E shows that 39,803 patients were hospitalized, whereas 169,912 were discharged home. Figure F presents the age distribution of all patients in the study, with a mean age of 41.7 years.
```{r, descriptive-statistics, echo=FALSE, message=FALSE, warning=FALSE}

combined_plots <- readRDS(
  file = here::here("subproject_bailey/output/combined_plots.rds")
)
combined_plots
```


